PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-08-30 txt/manuscript_short.tex
Attempt to improve text.

Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
group) and tests how much the output distribution obtained from the device running these circuits
differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
inverses (which should yield the identity circuit) and run those concatenated circuits on the
device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
\cite{forest-benchmarking}.

Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
characterizes capacity of a device for solving computational problems. It takes into account
multiple factors like number of qubits, connectivity and measurement errors. The Qiskit library
allows one to measure quantum volume of a device by using its \texttt{qiskit.ignis.verifica \\
tion.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
\cite{volume-in-practice}.

>>>>

Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
group) and tests how much the output distribution obtained from the device running these circuits
differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
inverses (which should yield the identity circuit) and run those concatenated circuits on the
device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
\cite{forest-benchmarking}. Another, equally popular, benchmarking method is
quantum tomography \cite{bantysh2021quantum}. Implementation of quantum tomography for
benchmarking NISQ devices can be found in \cite{tomography}.

In \cite{patel2020experimental}, the authors evaluated several IBM-Q machines using seven benchmarks
taking into account the errors and execution time.

QASMBench \cite{li2023qasmbench} is one of the first benchmark suites aiming at evaluating NISQ
devices using quantum applications from a broad range of domains, mainly using an approach based on
fidelity estimation. The benchmark presented in the paper compares the fidelity of execution among
the IBM-Q machines, the IonQ QPU and the Rigetti Aspen M-1 system.

Another quantity used for benchmarking NISQ devices is quantum volume. The quantum volume
characterizes the capacity of a device for solving computational problems. It takes into account
multiple factors like the number of qubits, connectivity and measurement errors. The Qiskit library
allows one to measure the quantum volume of a device by using its \texttt{qiskit.ignis.verification.quantum\_volume}. Other implementations of Quantum Volume can be found as well, see e.g.
\cite{volume-in-practice}.
